---
title: "linearmodel"
author: "Yuchen Hua"
date: "2022-11-25"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)

```

## fit a model
```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y= price, color = borough))+
  geom_point()
```

Let's fit the model 
```{r, include= FALSE}
fit = lm(price ~stars + borough, data = nyc_airbnb)
summary(fit)
summary(fit)$coef
residuals(fit)
```

Let's look at the result better ...(tidy out result)
```{r}
broom::glance(fit)

broom::tidy(fit) %>%
  select(-std.error, -statistic) %>%
  mutate(
    term = str_replace(term, "borough", "Borough:")
  ) %>%
  knitr::kable(digits = 3)
```

## Be in control of factors
```{r}
nyc_airbnb = 
  nyc_airbnb %>%
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

Look at that plot again

```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y= price, color = borough))+
  geom_point()
```

```{r}
fit = lm(price ~stars + borough, data = nyc_airbnb)

broom::tidy(fit)
broom::glance(fit)
```

## Diagnostics

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>%
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)
```

or can be written like
```{r}
nyc_airbnb %>%
modelr::add_residuals( fit) %>%
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)

nyc_airbnb %>%
  modelr::add_residuals( fit) %>%
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)
```

## Hypothesis test
This does t-test by default
```{r}
fit %>%
  broom::tidy()

```

What about the significantce of 'borough'
```{r}
fit_null = lm(price ~stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>%
  broom::tidy()
```

## Nest data, fit models
This is pretty formal and also complex
```{r}
fit = lm(price ~ stars*borough + room_type*borough, data= nyc_airbnb)

broom::tidy(fit)
```

This is more exploratary but maybe easier to understand
```{r}
nyc_airbnb %>%
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~stars, data =.x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(term == "stars")
```

or can be written as 
```{r}
nyc_airbnb %>%
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~stars, data =.x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(term != "(Intercept)")
```

```{r}
nyc_airbnb %>%
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~stars + room_type, data =.x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(term != "(Intercept)") %>%
  select(borough, term, estimate) %>%
  pivot_wider(
    names_from = borough,
    values_from = estimate
  )
```

Let's nest even more...
```{r}
nyc_airbnb %>%
  filter(borough =="Manhattan") %>%
  nest(data = -neighborhood) %>%
  mutate(
    models = map(.x = data, ~lm(price ~stars +room_type, data=.x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(str_detect(term, "room_type")) %>%
  ggplot(aes(x= neighborhood, y =estimate)) +
  geom_point() +
  facet_wrap(. ~term) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
  
```




